---
title: "Complex and Hypercomplex Neural Networks"
subtitle: "ft. Quaternions and friends"
author: "Carson Drake"
institute: "SMU DS7335"
date: "2019/12/01 (updated: `r Sys.Date()`)"
output:
  xaringan::moon_reader:
    css: [default, metropolis, metropolis-fonts]
    chakra: libs/remark-latest.min.js
    lib_dir: libs
    nature:
      beforeInit: "macros.js"
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r, load_refs, include=FALSE, cache=FALSE}
library(RefManageR)
BibOptions(check.entries = FALSE,
           bib.style = "alphabetic",
           cite.style = 'authortitle',
           max.names= 1,
           style = "markdown",
           hyperlink = TRUE,
           dashed = FALSE)
myBib <- ReadBib("./bibliography.bib", check = FALSE)
```
`r AutoCite(myBib, "qsurvey")`
`r AutoCite(myBib, "andiva_2019")`


```{r child = '_01.Rmd'}
```


---
class: inverse, middle, center

# Other Options?

???
Is there anything else we can try to make 
deep learning better?  

What else can we 
besides what we've been trying?

---
class: inverse, middle, center
# Background

---
# Numbers

---
# Quaternions (History)

---
# Quaternion (Algebra)

---
class: inverse, middle, center
# Quaternion Valued <br/>Neural Networks

---
# Intro to QNN

---
# CNN vs QCNN

---
# LSTM vs QLSTM

---
class: inverse, middle, center
# QNN Research<br/>Examples

---
# Parcollet, Morchid, and Linarès et al.

---
# Speech Recognition

---
# Heterogeneous Image Processing

---
# R2H Layer (Real-to-Quaternion)

---
class: inverse, middle, center
# Going Forward...

```{r child = '_000.Rmd'}
```